%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont} 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Tianyu Cheng}{ \urlstyle{same}\url{http://www.cs.utexas.edu/\~jhcty11/} \\
\href{mailto:tianyu.cheng@utexas.edu}{tianyu.cheng@utexas.edu} | Phone (512).517.1107
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Texas}

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\descript{B.S. in Computer Science}
\location{May 2016 | Austin, TX}
College of Natural Science \\
Turing Scholars Program \\
\location{Major GPA: 3.87 / 4.0}
\sectionsep

\descript{B.S. in Mathematics}
\location{May 2016 | Austin, TX}
College of Natural Science \\
\location{Major GPA: 4.00 / 4.0}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Courses}

% \subsection{Undergraduate}
Operating Systems (In Progress) \\
Data Management (In Progress) \\
Programming Languages (In Progress) \\
Computer Organization \& Architecture \\
Contemporary Issues in CS \\
Data Structure \\
% {\footnotesize \textit{\textbf{(Proctor) }}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\begin{tabular}{ll}
\skillbar{C/C++}{0.65}
\skillbar{Java}{0.8}
\skillbar{C\#}{0.5}
\skillbar{Python}{0.7}
\end{tabular}

\sectionsep

\subsection{Web Development}
\begin{tabular}{ll}
\skillbar{HTML/CSS}{0.8}
\skillbar{JavaScript}{0.6}
\skillbar{CoffeeScript}{0.45}
\skillbar{Node.js}{0.5}
\skillbar{Django}{0.6}
\end{tabular}

\sectionsep

\subsection{Graphics \& Game}
\begin{tabular}{ll}
\skillbar{OpenGL}{0.7}
\skillbar{WebGL}{0.6}
\skillbar{GLSL}{0.35}
\skillbar{Unity}{0.35}
\end{tabular}

\sectionsep

\subsection{Others}
\begin{tabular}{ll}
\skillbar{Photoshop}{0.6}
\end{tabular}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/tycheng}{\custombold{tycheng}} \\
% LinkedIn: \href{www.linkedin.com/pub/tianyu-cheng/66/335/834/}{\custombold{tianyu-cheng}} \\
Homepage: \href{http://www.cs.utexas.edu/~jhcty11/}{\custombold{www.cs.utexas.edu/~jhcty11/}} \\

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Digital Media Institute}
\descript{| Student Technician }
\location{Jun.2014 – Present | Austin, TX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} 
\item Worked on the back-end OOP design and implementation of an educational game with Unity and C\#.
\item Developed several third-party tools to facilitate game data management in Python, and provides a sanity check of the validity of the data.
\item Refactored back-end codes to comply with MVC pattern.
\end{tightemize}
\sectionsep

\runsubsection{Shenzhen Fortunes Technology}
\descript{| Test Engineer}
\location{Jun.2008 – Sept.2008 | Shenzhen, Guangdong, China}
\begin{tightemize} 
\item Worked on module testing and code review in C++.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{3D Graphics Animation}
\descript{| OpenGL GLSL}
\begin{tightemize} 
\item A shader-based OpenGL program that renders animating MMD 3D models. It provides a basic scene manager and a MMD-based renderer for small graphics applications.
\item Currently being ported to web platform using WebGL and CoffeeScript.
\end{tightemize}
\sectionsep

\runsubsection{Online Linear Algebra Solver}
\descript{| Python Django}
\begin{tightemize} 
\item Many high school students are getting ahead in Mathematics. This project aims to help students learn linear algebra by examples. 
\item Dynamically solve problems and show the individual steps of how they are solved. The supported problems include row reduction, matrix multiplication, inverse of matrices, eigenvalue, and diagonalization.
\end{tightemize}
\sectionsep

\runsubsection{Online Law Case Manager}
\descript{| Office Automation}
\begin{tightemize} 
\item Law cases management generally involves repetitive operation. This project aims to simplify the procedure.
\item Implemented with Python, Karrigell and MySQL. 
\item Provides an easy-to-use UI for users to archive, modify and delete law case records. It also generates law case documents for printing.
\end{tightemize}
\sectionsep

\runsubsection{Online Website Designer}
\descript{| User Experience}
\begin{tightemize} 
\item This project owes the inspiration to online website editing tools, e.g. Weebly and Yola. 
\item Implemented with Java Struts, HTML/CSS and JavaScript. 
\item Creates a user-friendly interface to customize websites by drag-and-drop.
\end{tightemize}
\sectionsep

\runsubsection{Desktop Task Reminder}
\descript{| Qt Sprite}
\begin{tightemize} 
\item This project is a birthday present for my mother.
\item Implemented with Qt for GUI and sqlite3 for task management.
\item Provides a customizable notification system and sends out notifications asking user to rest every two hours.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
